Comparing Predicted Boundaries vs Called Boundaries

### 2019-08-02 Scripts/comparing_predicted_vs_called_boundary_regions.Rmd
edits

res <- makeVennDiagram(Peaks=list(toptfbs_10_gm12878_chr22[[3]], toptfbs_10_gm12878_chr22[[4]]),
                       NameOfPeaks=c("Called", "Predicted"),
                       connectedPeaks = "keepAll")
venn_gm12878_22 <- venn_cnt2venn(res$vennCounts)
venn_gm12878_22 <- compute.Venn(venn_gm12878_22)
gp <- VennThemes(venn_gm12878_22)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
gp[["FaceText"]][["10"]]$cex <- 2
gp[["FaceText"]][["11"]]$cex <- 2
gp[["FaceText"]][["01"]]$cex <- 2
gp[["SetText"]][["Set1"]]$cex <- 2
gp[["SetText"]][["Set2"]]$cex <- 2
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_5kb, 
                                                 gp = gp, 
                                                 show=list(Universe=FALSE))), 
                        top=textGrob("Boundary Region", 
                                     gp=gpar(fontsize=50)))

>>>>

res <- makeVennDiagram(Peaks=list(toptfbs_10_gm12878_chr22[[3]], toptfbs_10_gm12878_chr22[[4]]),
                       NameOfPeaks=c("Called", "Predicted"),
                       connectedPeaks = "keepAll")
venn_gm12878_22 <- venn_cnt2venn(res$vennCounts)
venn_gm12878_22 <- compute.Venn(venn_gm12878_22)
gp <- VennThemes(venn_gm12878_22)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
gp[["FaceText"]][["10"]]$cex <- 2
gp[["FaceText"]][["11"]]$cex <- 2
gp[["FaceText"]][["01"]]$cex <- 2
gp[["SetText"]][["Set1"]]$cex <- 2
gp[["SetText"]][["Set2"]]$cex <- 2
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_gm12878_22, 
                                                 gp = gp, 
                                                 show=list(Universe=FALSE))), 
                        top=textGrob("Boundary Region", 
                                     gp=gpar(fontsize=50)))
